This first chapter introduces some notions that weren't formalize in
mathlib about representation theory. The main goal of this part is to build
the induced representation in a particular case and the Frobenius reciprocity
in a particular case.

\section{Group algebra}

\begin{definition}
    \label{def:trivialHG}
    \uses{}
    \lean{kG_kH_Module.mulHom_mapHG}
    \leanok
    Given $G$ a group and $H$ a subgroup of $G$, we have a trivial homomorphism from $H$
    to $G$ given by $h\mapsto h$.
    \begin{proof}
        \leanok
        Trivial.
    \end{proof}
\end{definition}

\begin{definition}
    \label{def:trivialkHkG}
    \uses{}
    \lean{kG_kH_Module.Map_KHKG}
    \leanok
    Given $\mathbb{K}$ a field, $G$ a group and $H$ a subgroup of $G$, 
    we have a trivial homomorphism from $\mathbb{K}[H]$ to $\mathbb{K}[G]$.
    \begin{proof}
        \leanok
        Trivial.
    \end{proof}
\end{definition}


\begin{proposition}
    \label{prop:KGcommsemiring}
    \uses{}
    \lean{kG_kH_Module.KGCommRing}
    \leanok
    If $G$ is a commutative group, then $\mathbb{K}[G]$ is a commutative semiring.
\end{proposition}
\begin{proof}
    \leanok
    Trivial.
\end{proof}

\begin{definition}
    \label{prop:KHKGsmul}
    \uses{def:trivialkHkG}
    \lean{kG_kH_Module.SMulKHKG}
    \leanok
    If $H$ is a commutative subgroup of $G$, we have a scalar multiplication
    of $\mathbb{K}[H]$ on $\mathbb{K}[G]$ given by the classic multiplication
    on $\mathbb{K}[G]$.
\end{definition}

\begin{definition}
    \label{def:RingHomkHkG}
    \uses{def:trivialHG,prop:KGcommsemiring}
    \lean{kG_kH_Module.RingMorphism_KH_KG}
    \leanok
    If $H$ is a commutative subgroup of $G$, we have a ring homomorphism
    from $\mathbb{K}[H]$ to $\mathbb{K}[G]$ given by the map defined in \ref{def:trivialHG}.
\end{definition}
\begin{proof}
    \leanok
    Trivial.
\end{proof}

\begin{proposition}
    \label{prop:kG_is_kH_Algebra}
    \uses{def:RingHomkHkG}
    \lean{kG_kH_Module.KG_is_KcenterG_Algebra}
    \leanok
    We have that $\mathbb{K}[G]$ is a $\mathbb{K}[\mathcal{Z}_G]$
    algebra, where $\mathcal{Z}_G$ is the center of $G$
\end{proposition}
\begin{proof}
    \leanok
    We check the axioms of an algebra. Nothing really difficult.
\end{proof}